Cannibalism among the supermassive black holes

### 2016-08-25 paper.tex
added plots

\section{Methods}\label{sec:methods}

@@

\section{Results}\label{sec:results}

@@

\begin{figure}
\centering
%\includegraphics[width=0.45\textwidth]{plots/plot1.png}
\caption{This is a caption.}
\label{this_is_a_label}
\end{figure}

@@

\subsection{Stalling SMBHs in the halo}

>>>>

\section{Methods}\label{sec:methods}
\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_1.png}
\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_65.png}\\
\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_187.png}
\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_217.png}\\
\caption{default}
\label{default}
\end{center}
\end{figure*}

@@

\section{Results}\label{sec:results}
\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_1.png}
\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_65.png}\\
\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_187.png}
\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_217.png}\\
\caption{default}
\label{default}
\end{center}
\end{figure*}

@@

@@

\subsection{Stalling SMBHs in the halo}
\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/t_at_center_histogram_gal_1.png}
\includegraphics[width=0.45\textwidth]{plots/t_at_center_histogram_gal_65.png}\\
\includegraphics[width=0.45\textwidth]{plots/t_at_center_histogram_gal_187.png}
\includegraphics[width=0.45\textwidth]{plots/t_at_center_histogram_gal_217.png}\\
\caption{default}
\label{default}
\end{center}
\end{figure*}
